\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
%
\item  Verify that the set of complex numbers numbers described in the form of c where x and y are rational is a sub-field of C.
\\
\solution
\input{./solutions/1/1/1/solution.tex}
\item Let $\mathbb{F}$ be the field of complex numbers. Are the following two systems of linear equations equivalent? If so, express each equation in each system as a linear combination of the equations in the other system.
\begin{align*}
    x_1 - x_2 &=0\\
    2x_1 + x_2 &=0
\end{align*}
and 
\begin{align*}
    3x_1 + x_2 &=0 \\
    x_1 + x_2 &=0
\end{align*}
%
\solution
\input{./solutions/1/1/2/solution.tex}

\item Are the following two systems of linear equations equivalent?
\begin{equation} \label{eq:solutions/1/1/3/eq:eq1}
\begin{split}
    -x_1+x_2+4x_3=0\\
    x_1+3x_2+8x_3=0\\
    \frac{1}{2}x_1+x_2+\frac{5}{2}x_3=0
\end{split}
\end{equation}
\solution
\input{./solutions/1/1/3/solution.tex}
%
\item Let $\mathbb{F}$  be the field of complex numbers. Are the following two systems of linear equations equivalent? If so, express each equation in each system as a linear combination of equations in other system. First system of equations:
\begin{align}
2x_1+(-1+i)x_2+x_4=0\\
3x_2-2ix_3+5x_4=0
\end{align}
The second system of equations:
\begin{align}
(1+\frac{i}{2})x_1+8x_2-ix_3-x_4=0\\
\frac{2}{3}x_1-\frac{1}{2}x_2+x_3+7x_4=0
\end{align}
%
\solution
\input{./solutions/1/1/4/solution.tex}
\item Let $\mathbb{F}$ be a set which contains exactly two elements,0 and 1.Define an addition and multiplication by tables.
\begin{table}[h!]
  \begin{center}
    \label{eq:solutions/1/1/5/tab:table1}
    \begin{tabular}{l|c|r}
      + & 0 & 1 \\
      \hline
      0 & 0 & 1\\
      1 & 1 & 0
    \end{tabular}
  \end{center}
\end{table}
\begin{table}[h!]
  \begin{center}
    \label{eq:solutions/1/1/5/tab:table2}
    \begin{tabular}{l|c|r}
      $\cdot$ & 0 & 1 \\
      \hline
      0 & 0 & 0\\
      1 & 0 & 1
    \end{tabular}
  \end{center}
\end{table}
  Verify that the set $\mathbb{F}$, together with these two operations, is a field.
%
\\
\solution
\input{./solutions/1/1/5/solution.tex}
\item Prove that if two homogenous systems of linear equations in two unknowns have the same solutions, then they are equivalent.
\\
\solution
\input{./solutions/1/1/6/solution.tex}
\item Prove that each subfield of the field of complex number contains every rational number
\\
\solution
\input{./solutions/1/1/7/solution.tex}
%
\item Prove that, each field of the characteristic zero contains a copy of the rational number field.
\\
\solution
\input{./solutions/1/1/8/solution.tex}
\end{enumerate}


