\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
%
\item  Find weather given  functions \textbf{T} from $\mathbb{R}^2$ into $\mathbb{R}^2$ are linear transformations or not

\begin{enumerate}
\item 
\begin{align}
    T\myvec{x_1\\x_2}=\myvec{1+x_1\\x_2}
\label{eq:solutions/3/1/1/a/1}
\end{align}
\solution
\input{./solutions/3/1/1/a/solution.tex}
%
\item \begin{align}
\vec{T}\myvec{x_1\\x_2}= \myvec{x_2\\ x_1} \label{eq:solutions/3/1/1/b/0}
\end{align}
Does function $\vec{T}$ from $\mathbb{R}^2$ into $\mathbb{R}^2$ is Linear Transformation.

\solution
\input{./solutions/3/1/1/b/solution.tex}
%
\item 
\begin{align}
	\textbf{T}(x_1,x_2) = ({x_1}^2,x_2)
\end{align}

\solution
\input{./solutions/3/1/1/c/solution.tex}
%
\item Is the following function $\vec{T}$ from $\mathbb{R}^2$ into $\mathbb{R}^2$  is linear transformation?
\begin{align}
\vec{T} 
\myvec{
x_1\\
x_2}
= 
\myvec{\sin (x_1)\\x_2} \nonumber\end{align}
%
%
\solution
\input{./solutions/3/1/1/d/solution.tex}
%
\item Verify whether $T(x_1, x_2)  = (x_1 - x_2, 0)$ is a linear transformation or not.
%
\solution
\input{./solutions/3/1/1/e/solution.tex}

\end{enumerate}
%
\item Find the range, rank, null space, and nullity for the zero transformation and the identity transformation on a finite-dimensional space V. 
%
\\
\solution
\input{./solutions/3/1/2/solution.tex}

\item \begin{enumerate}[label=\emph{\alph*)}]
\item
Let $\vec{F}$ be a field and let $\vec{V}$ be the space of polynomial functions $f$ from $\vec{F}$
into $\vec{F}$, given by
\begin{align*}
	f(x)=c_0+c_1x+\cdots +c_nx^n
\end{align*}
Let $\vec{D}$ be a linear differentiation transformation defined as
\begin{align*}
	(\vec{D}f)(x)=\frac{df(x)}{dx}
\end{align*}
Then find the range and null space of 
$\vec{D}$.\\
\item
Let $\vec{R}$ be the field of real numbers and let $\vec{V}$ be the space of all functions from 
$\vec{R}$ into $\vec{R}$ which are continous. Let $\vec{T}$ be linear transformation defined by
\begin{align*}
	(\vec{T}f)(x)=\int_{0}^{x} f(t)\,dt
\end{align*}
Find the range and null space of $\vec{T}$.
\end{enumerate}
%
\solution
\input{./solutions/3/1/3/solution.tex}
%
\item Describe explicitly the linear transformation T from $\mathbb{F}^2$ into $\mathbb{F}^2$ such that  $T(\epsilon_1 )=(a,b),T(\epsilon_2 )=(c,d)$.
%
\solution
\input{./solutions/3/1/6/solution.tex}
%
\item Let $\mathbb{F}$ be a subfield of the complex numbers and let $\mathbb{T}$ be the function from $\mathbb{F}^3$ into $\mathbb{F}^3$ defined by 
\begin{align}
    \mathbb{T}(x_1,x_2,x_3)=\\(x_1-x_2+2x_3,2x_1+x_2,-x_1-2x_2+2x_3)
\end{align}
\begin{enumerate}
\item  Verify that $\mathbb{T}$ is a linear transformation.\\
\item  If $(a,b,c)$ is a vector in  $\mathbb{F}^3$, what are the conditions on $a,b,c$ that the vector be in the range of  $\mathbb{T}$ ?What is the rank of  $\mathbb{T}$?\\
\item  What are the conditions on $a,b,c$ that $(a,b,c)$ be in the null space of  
$\mathbb{T}$? What is the nullity of  $\mathbb{T}$?
\end{enumerate}
\solution
\input{./solutions/3/1/7/solution.tex}
\item Describe explicitly a linear transformation from $R^{3}$ into $R^{3}$ which has as its range the subspace spanned by \myvec{1&0&-1} and \myvec{1&2&2}.  
%
\\
\solution
\input{./solutions/3/1/8/solution.tex}
\item Let $\vec{V}$ be the vector space of all $n \times n$ matrices over the field $\mathbb{F}$, and let $\vec{B}$ be a fixed $n \times n$ matrix. If a transformation $T$ defined as follows,
\begin{align*}
    T(\vec{A}) &= \vec{AB} - \vec{BA}
\end{align*}
Prove that $T$ is a linear transformation from $\vec{V}$ into $\vec{V}$
%
\solution
\input{./solutions/3/1/9/solution.tex}
%
\item Let V be the set of all complex numbers regarded as a vector space over the field of real numbers(usual operations). Find a function from V into V which is a linear transformation on the above vector space, but which is not a linear transformation on $\mathbb{C}$ i.e., which is not complex linear.
%
\\
\solution
\input{./solutions/3/1/10/solution.tex}
%
\item Let $\vec{V}$ be the space of $n \times 1$ matrices over $F$ and let $\vec{W}$ be the space of $m \times 1$ matrices over $F$. Let $\vec{A}$ be a fixed $m \times n$ matrix over $F$ and let $T$ be the linear transformation from $\vec{V}$ into $\vec{W}$ defined by $T(\vec{X}) = \vec{A}\vec{X}$. Prove that $T$ is the zero transformation if and only if $\vec{A}$ is the zero matrix.
%
\solution
\input{./solutions/3/1/11/solution.tex}
%
\item Let $\vec{V}$ be an $n$-dimensional vector space over the field $\vec{F}$ and let $\vec{T}$ be a linear transformation from $\vec{V}$ into $\vec{V}$ such that the range and null space of $\vec{T}$ are identical. Prove that $n$ is even. (Can you give an example of such a linear transformation $\vec{T}$)?
%
\\
\solution
\input{./solutions/3/1/12/solution.tex}
\end{enumerate}
