\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}


\item In each of the following cases, let $T$ be the linear operator on $R^2$ which is represented by matrix $A$ in the standard ordered basis for $R^2$, and let $U$ be the linear operator on $C^2$ represented by $A$ in the standard ordered basis. Find the characteristic polynomial for $T$ and that for $U$, find the characteristic value of each operator, and for each characteristic value $c$ find a basis for the corresponding space of characteristic vectors.
\begin{align}
    \vec{A_1} &= \myvec{1&0\\
                     0&0}\\
    \vec{A_2} &= \myvec{2&3\\
                     -1&1}\\
    \vec{A_3} &= \myvec{1&1\\
                     1&1}
\end{align}     
%
%
\\
\solution
\input{./solutions/6/2/1/solution.tex}
\item Let T be the linear operator on $\vec{R}^3$ which is represented in the standard ordered basis by the matrix
\begin{align}
\myvec{-9&4&4\\-8&3&4\\-16&8&7}
\label{eq:solutions/6/2/4/Q}
\end{align}
Prove that T is diagonalizable by exhibiting a basis for $\vec{R}^3$, each vector of which is a characteristic vector of T. 
%
%
\\
\solution
\input{./solutions/6/2/4/solution.tex}
\item Let
\begin{align}
\vec{A}=\myvec{6&-3&-2\\4&-1&-2\\10&-5&-3}
\end{align}
Is $A$ similar over the field $R$ to a diagonal matrix ? \\Is $A$ similar over the field C to a diagonal matrix?
%
%
\\
\solution
\input{./solutions/6/2/5/solution.tex}
\twocolumn
\item 	Let $\mathbf{T}$ be the linear operator on $\mathbf{R}^{4}$ which is represented in the standard basis by the matrix \\
	\begin{align}
	    \myvec{0&0&0&0 \\ a&0&0&0 \\ 0&b&0&0 \\ 0&0&c&0} 
	\end{align}
	
	Under what conditions on $a$, $b$ and $c$ in $\mathbf{T}$ is diagonalizable?
%
\\
\solution
\input{./solutions/6/2/6/solution.tex}
\twocolumn
\item Let $\vec{T}$ be the linear operator on a $n-$ dimensional vector space $\vec{V}$ and suppose that  $\vec{T}$ has an n distinct characteristic values.Prove that $\vec{T}$ is diagonalizable.
%
\\
\solution
\input{./solutions/6/2/7/solution.tex}
\twocolumn
\item Let $\vec{A}$ and $\vec{B}$ be $n\times n$ matrices over the field $F$.Prove that if $\brak{\vec{I}-\vec{A}\vec{B}}$ is invertibe
\begin{enumerate}
    \item $\brak{\vec{I}-\vec{B}\vec{A}}$ is invertible and
    \item $\brak{\vec{I}-\vec{B}\vec{A}}^{-1}=\vec{I}+\vec{B}\brak{\vec{I}-\vec{A}\vec{B}}^{-1}\vec{A}$
\end{enumerate}
%
\solution
\input{./solutions/6/2/8/solution.tex}
\item Usig the result of the previous exercise, prove that, if $A$ and $B$ are $n \times n$ matrices over the field $F$, then $AB$ and $BA$ have precisely the same characteristic values.
%
\solution
\input{./solutions/6/2/9/solution.tex}
\item Suppose that $\vec{A}$ is a $2\times2$ matrix with real entries which is symmetric $\brak{\vec{A}^t=\vec{A}}$.
Prove that $\vec{A}$ is similar over $\mathbb{R}$ to a diagonal matrix. 
%
\\
\solution
\input{./solutions/6/2/10/solution.tex}
\twocolumn
\item Let $\vec{N}$ be a 2 × 2 complex matrix such that $\vec{N}^2$ = 0. Prove that either $\vec{N}$ = 0 or $\vec{N}$ is similar over $\mathbb{C}$ to\\
\begin{align}
\myvec{0&0\\1&0}
\end{align}
%
\\
\solution
\input{./solutions/6/2/11/solution.tex}
\twocolumn
\item Let $A$ be the an $n \times n$ diagonal matrix with characteristic polynomial
\begin{align}
(x-c_1)^{d_1} (x-c_2)^{d_2} \dots (x-c_k)^{d_k} \label{eq:solutions/6/2/14/1.1}
\end{align}
Where $c_1, c_2,  \dots c_k $ are distinct. Let $\mathbf{V}$ the space of $n \times n$ matrices $B$ such that 
\begin{align}
AB = BA \label{eq:solutions/6/2/14/1.2}
\end{align}
Prove that the dimension of $\mathbf{V}$ is,
\begin{align}
{d_1}^2 + {d_2}^2 \dots + {d_k}^2 \label{eq:solutions/6/2/14/1.3}
\end{align}
%
\\
\solution
\input{./solutions/6/2/14/solution.tex}
\item Let $\vec{V}$ be the space of $n \times n$ matrices over $F$. Let $\vec{A}$ be a fixed $n \times n$ matrix over $F$. Let $\vec{T}$ be the linear operator 'left multiplication by $\vec{A}$' on $\vec{V}$. Is it true that $\vec{A}$ and $\vec{T}$ have the same characteristic values?
%
\\
\solution
\input{./solutions/6/2/15/solution.tex}
\end{enumerate}
